Constraint Programming - Inside Gecode

### 2014-05-05 paper.tex
fixed references

\newcommand{\reffig}[1]{{[Fig.~\ref{#1}.]}}
\newcommand{\refeq}[1]{{[Eq.~\ref{#1}.]}}

@@

	Hence there are boolean variables available it is also possible to use logical operators to combine other constraint types to logical expressions. To show the usage of this on an example I will give the implementation for the placement of two squares such that they do not overlap \reffig{fig:squares}. This problem can be expressed mathematically by \cite[p. 101]{programmingGecode}
	\begin{equation}
	\begin{split}
		x_1 + d_1 \le x_2 & \lor x_2 + d_2 \le x_1 \lor \\
		y_1 + d_1 \le y_2 & \lor y_2 + d_2 \le y_1
	\end{split}
	\end{equation}
	and in \emph{Gecode} by
	\begin{lstlisting}
rel(home,	(x1 + d1 <= x2) || 
		(x2 + d2 <= x1) || 
		(y1 + d1 <= y2) || 
		(y2 + d2 <= y1));
	\end{lstlisting}
	which is again quite obvious to a reader with some experience in a C-like programming language.

@@

	To visualize this effect consider a constraint problem based on two variables $x \in \{1, 5, 6\}$ and $y \in \{1, 2\}$ and one constraint based on them.
	\begin{equation}
		c_1:\ x \le y
	\end{equation}
	Without constraint propagation and branching first on $x$ this results in search tree \reffig{fig:bigTree}. Obviously the right parts of this tree can already be pruned already at the root by propagation of constraint $c_1$ and therefore it is not necessary to create and evaluate these subtrees \reffig{fig:smallTree}.

>>>>

\newcommand{\reffig}[1]{{figure \ref{#1}}}
\newcommand{\refeq}[1]{{(\ref{#1})}}

@@

	Hence there are boolean variables available it is also possible to use logical operators to combine other constraint types to logical expressions. To show the usage of this on an example I will give the implementation for the placement of two squares such that they do not overlap. The related variables are defined in \reffig{fig:squares}. This problem can be expressed mathematically by \cite[p. 101]{programmingGecode}
	\begin{equation}
	\begin{split}
		x_1 + d_1 \le x_2 & \lor x_2 + d_2 \le x_1 \lor \\
		y_1 + d_1 \le y_2 & \lor y_2 + d_2 \le y_1
	\end{split}
	\end{equation}
	and in \emph{Gecode} by
	\begin{lstlisting}
rel(home,	(x1 + d1 <= x2) || 
		(x2 + d2 <= x1) || 
		(y1 + d1 <= y2) || 
		(y2 + d2 <= y1));
	\end{lstlisting}
	which is again quite obvious to a reader with some experience in a C-like programming language.

@@

	To visualize this effect consider a constraint problem based on two variables $x \in \{1, 5, 6\}$ and $y \in \{1, 2\}$ and one constraint based on them.
	\begin{equation}
		c_1:\ x \le y
	\end{equation}
	Without constraint propagation and branching first on $x$ the search trees turns out to be the one in \reffig{fig:bigTree}. Obviously the right parts of this tree can already be pruned already at the root by propagation of constraint $c_1$ and therefore it is not necessary to create and evaluate these subtrees like in \reffig{fig:smallTree}.
